---
title: "FEV1 variability"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## target knits Rmds in their own session, so load libraries here.
## source("../packages.R")
```

## Analysis

Linear models were fitted to the `image_metrics` data. Each model included progressive adjustment. Partial $R^2$ statistics were computed for terms in these models using the `rsq` package. The method used to compute each partial $R^2$ statistic is from Zhang, 2017.

```{r}
tar_load(model_table)

model_table

```

## References

Zhang, D. (2017). A coefficient of determination for generalized linear models. __The American Statistician__, 71(4): 310-316.

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
# if(requireNamespace('git2r', quietly = TRUE)) {
#   git2r::repository()
# } else {
#   c(
#     system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
#     system2("git", args = c("remote", "-v"), stdout = TRUE)
#   )
# }

## session info
sessionInfo()
```

</details>
